%-------------------------
% License : MIT
% Based on https://github.com/sb2nov/resume
% from Sourabh Bajaj
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Joshua Martínez} & Email : \href{mailto:djoshuamartinezpineda@gmail.com}{djoshuamartinezpineda@gmail.com}\\
  Website: \href{https://mynjj.github.io}{https://mynjj.github.io} &  \\
\end{tabular*}

\section{Profile}
Hardworking passionate profesional, currently studying a Msc. in Computer Science. With experience
in software development, which taught me to translate my hard-skills to useful
products. Highly responsible on my work. Excited to learn more, try new
things, face challenges, and to help.

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IT University}{Copenhaguen, Denmark}
      {Master of Science in Computer Science; Gr: 12/12}{Aug. 2020 -- Present}
    \resumeSubheading
      {Universidad La Salle}{Mexico City, Mexico}
      {Bachelor of Engineering in Electronics and Communications;  GPA: 4 (9.76/10.0)}{Aug. 2012 -- Nov. 2016}
    \resumeSubheading
      {Universidad Nacional Autónoma de México}{Mexico City, Mexico}
      {Bachelor of Mathematics}{Aug. 2014 -- Jul. 2018}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {ABaCus DK}{Copenhagen, Denmark}
      {Student Developer}{Nov. 2020 - Present}
      \vspace{3pt}

      I learned to work in a different culture, exploring a software developed
      by several people, with different work styles. Employment is time
      limited, but I was able to contribute on the system. See recommendation attached.

      \resumeItemListStart
      \resumeItem{Features, bug fixes for main product}
        {Wrote fixes for minor bugs. Also the frontend and backend for pages
          displaying statistics for the teacher and students. The project used
          PHP/Symfony, JS/React.}
      \resumeItemListEnd

    \resumeSubheading
      {TIDE}{Mexico City, Mexico}
      {Software Engineer}{Jan. 2019 - Aug. 2020}
      \vspace{3pt}

      I developed many useful skills, learned to deliver fully functional
      products and to take responsability for them as a team. Designed and implemented
      creative solutions with several technologies.
      \resumeItemListStart
        \resumeItem{Employee time clock}
          {Raspberry Pi's with multiple identification and synchronization features. Integrated
            sensors SDK's (C/Java), implemented features for the main service
            (Node.js), and UI(React)}
        \resumeItem{Airport Lounge app}
          {Android/iOS app with React Native. Several features, integrated to an
          existing backend and created a backend-for-frontend for other features
          (Node.js/sails.js). Other technologies used: Redux, Firebase FCM}
        \resumeItem{Scotiabank's online pride parade}
        {Basic MMORPG for 2020's stay@home Pride Parade. AWS/EC2 instances
          running a Phaser.js game, connecting to WebSocket servers (Typescript). Redis 
          used for chat features.}
        \resumeItem{IOT devices monitor}
          {Utilities to provide software updates, remote SSH access and stats
            recopilation for remote technical support. Implemented features on
            both sides (Node.js, PHP/Symfony, React, Linux scripting).}
        \resumeItem{Coca-cola promotional game}
          {Soccer game for marketing stands of Coca-cola running on Raspberry Pi's,
            controlled by a Wii controller. Created with Python/Pygame.}
        \resumeItem{Airport Lounge software}
          {Software spanning several company areas. Implemented several
            features, on both backend (PHP/Symfony) and frontend (React/Redux).}
        \resumeItem{Restaurant software}
          {Highly customized restaurant software. Implemented several features,
            on both backend (PHP/Symfony) and frontend (React/Redux).}
      \resumeItemListEnd

    \resumeSubheading
      {VtSoftware}{Playa del Carmen, Mexico}
      {Software Engineer}{Jun. 2017 - May 2018}
      \vspace{3pt}

      I learned how to translate my academic knowledge to useful software. One
      of the most important skills I learned is to listen to the client
      requirements and design accordingly.

      \resumeItemListStart
        \resumeItem{Vacation Clubs Payroll Software}
          {Modeled and designed according to customer needs. Bootstraped
            project on PHP/Laravel and Vue.js, integrated to an existing sales
            system DB. Also wrote some SQLServer stored procedures.}
        \resumeItem{Hotel Inventory Software}
          {Modeled and designed according to customer needs. Bootstraped project
          on PHP/Laravel and jQuery.}
      \resumeItemListEnd

    \resumeSubheading
      {École de Technologie Supérieure}{Montreal, Canada}
      {Research Internship}{Apr. 2015 - Jul. 2015}
      \resumeItemListStart
        \resumeItem{Estimation of disparity on GPUs}
          {Research on disparity estimation algorithms and implementation on
            Matlab and then using C/CUDA}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Other experience}
\resumeSubHeadingListStart
\resumeSubItem{Teaching activities}{Private tutor on mathematics and
  programming, mostly focusing on kids (from 9 to 16). Social Service as an
  English teacher for adults.}
\resumeSubHeadingListEnd


\section{Academic activities}
  \resumeSubHeadingListStart
    \resumeSubItem{ANFEI's award}{Highest GPA on engineering faculty. Graduated with
      Magna Cum Laude.}
    \resumeSubItem{Robotics Winter School. 2013}{INAOE, Puebla, Mexico.}
    \resumeSubItem{Robotics competitions. 2011 - 2013}
      {Participation on Robocup, LARC competitions with the school robotics team
        (Cyberlords). Istanbul, Turkey and Mexico City. Our team achieved good
        results.}
    \resumeSubItem{Programming competitions.}
      {IEEExtreme Programming competitions. Good results on our region.}
  \resumeSubHeadingListEnd

  \section{Skills I've worked with}
  \vspace{-30pt}
\begin{tabular}{p{9cm}p{9cm}}
  \section{Programming Languages}
  JS, TS, Node.js, Python, C, Java, SQL, PHP, Matlab
  \hfill &

  \section{Technologies}
    \resumeItemListStart
    \resumeSubItem{Frontend:}{React, Redux, React Native, Vue.js, Phaser, eCharts.}
    \resumeSubItem{Backend:}{Laravel, Symfony, Redis, Socket.io, Express, Sails.js}
    \resumeSubItem{Other:}{Linux, Raspberry Pi, AWS, Git, SVN, Nginx}
    \resumeItemListEnd
  \end{tabular}

  \section{Other skills (Coursework \& others)}
    Scala, C++, Microchip PIC Assembler, Arduino, Eagle.

  \section{Languages}
  \resumeItemListStart
  \resumeSubItem{Spanish}{Native}
  \resumeSubItem{English}{Fluent. TOEFL iBT(115/120)}
  \resumeItemListEnd


\end{document}
